RepData_PeerAssessment1
=======================
## Loading and preprocessing the data

```{r}
data<-read.csv("activity.csv")
```

## What is mean total number of steps taken per day?

### Histogram of the total number of steps taken each day:

```{r}
d<-data[rowSums(is.na(data))==0,]
dates<-unique(d$date)
steps<-c()
for (arg in dates){
steps<-c(steps,sum(d[d$date==arg,]$steps[!is.na(d[d$date==arg,]$steps)]))
}

hist(steps)
```

### Mean total number of steps taken per day:
```{r}
mean(steps)
```
### Median total number of steps taken per day:
```{r}
median(steps)
```

## What is the average daily activity pattern?

### Time series plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r}
intervals<-unique(d$interval)
steps2<-c()
for (arg in intervals){
steps2<-c(steps2,mean(d[d$interval==arg,]$steps[!is.na(d[d$interval==arg,]$steps)]))
}
plot(intervals,steps2,type="l",ylab="steps",main="Time series plot")

```

### The 5-minute interval that contains the maximum number of steps:
```{r}
temp<-cbind(intervals,steps2)
temp[ order(-temp[,2]), ][1]
```


## Imputing missing values

### Calculate and report the total number of missing values in the dataset

```{r}
length(data$steps)-length(d$steps)
```

### Devise a strategy for filling in all of the missing values in the dataset
Strategy: Using the mean for that 5-minute interval to fill in missing value

### Create a new dataset that is equal to the original dataset but with the missing data filled in.

```{r}
names(steps2)<-intervals
steps3<-data$steps
intervals3<-data$intervals
for (i in 1:length(steps3)){
if (is.na(steps3[[i]])) steps3[[i]]<-steps2[toString(intervals3[[i]])]
}
data2<-data
data2$steps<-steps3
```

### New histogram of the total number of steps taken each day:

```{r}
dates<-unique(d$date)
steps<-c()
for (arg in dates){
steps<-c(steps,sum(d[d$date==arg,]$steps[!is.na(d[d$date==arg,]$steps)]))
}

hist(steps)
```

### New mean total number of steps taken per day:
```{r}
mean(steps)
```
### New median total number of steps taken per day:
```{r}
median(steps)
```

### Do these values differ from the estimates from the first part of the assignment? 
No
### What is the impact of imputing missing data on the estimates of the total daily number of steps?
If you use the mean for that 5-minute interval to fill in missing value, nothing changes.

## Are there differences in activity patterns between weekdays and weekends?

### Create a new factor variable in the dataset with two levels – “weekday” and “weekend” indicating whether a given date is a weekday or weekend day.

```{r}
weekday<-c()
for (day in data2$date){
weekday<-c(weekday,weekdays(as.Date(day)))
}
for (i in 1:length(weekday)){
if (weekday[i]  %in% c("Sunday","Saturday")){weekday[i]<-"weekend"}else{weekday[i]<-"weekday"}
}
data2$weekday <- weekday

```

### Time series plot

```{r}

d<-data2
intervals<-unique(data2$interval)
steps2a<-c()
steps2b<-c()
d2a<-d[d$weekday=="weekday",]
d2b<-d[d$weekday=="weekend",]
for (arg in intervals){
steps2a<-c(steps2a,mean(d2a[d2a$interval==arg,]$steps[!is.na(d2a[d2a$interval==arg,]$steps)]))
}
for (arg in intervals){
steps2b<-c(steps2b,mean(d2b[d2b$interval==arg,]$steps[!is.na(d2b[d2b$interval==arg,]$steps)]))
}

plot(intervals,steps2a,type="l",ylab="steps",main="weekday")

plot(intervals,steps2a,type="l",ylab="steps",main="weekend")


```
